%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Raasikh Kanjiani} \\ \vspace{1pt}
    \small 404-428-8533 $|$ \href{mailto:raasikh.kanjiani@gmail.com}{raasikh.kanjiani@gmail.com} $|$ 
    \href{https://linkedin.com/in/raasikhk}{linkedin.com/in/raasikhk} $|$
    \href{https://github.com/Student9676}{github.com/Student9676}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Emory University}{Atlanta, GA}
      {Bachelor of Science in Computer Science, Minor in Mathematics}{Aug. 2023 -- May 2026}
        \vspace{0pt}
      \resumeSubheading
      {University of Georgia}{Athens, GA}
      {Bachelor of Science in Computer Science, New Media Certificate}{Aug. 2022 -- May 2023}
      \vspace{1pt}
    \small{\item{
     \textbf{Coursework}{: Data Structures and Algorithms, Artificial Intelligence, Machine Learning, Systems Programming, Computer Architecture} \\ 
     \vspace{4pt}
     \textbf{Programming Languages}{: Java (Advanced), Python (Advanced), Swift (Intermediate), C (Intermediate),\newline R (Intermediate), Assembly, JavaScript, SQL, Lua, Latex}
    }}
    
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Research Intern (REU)}{June 2022 -- Present}
      {Emory University}{Atlanta, GA}
      \resumeItemListStart
        \resumeItem{Develop a scientific contribution aware literature review generation model by incorporating a graph neural network with 690,000+ papers and 10,000+ literature reviews.}
        \resumeItem{Research appropriate summarization evaluation frameworks and metrics to quantify model performance.}
      \resumeItemListEnd

    \resumeSubheading
      {iOS App Development Intern}{Jan. 2024 -- May 2024}
      {USA Boccia}{Remote}
      \resumeItemListStart
        \resumeItem{Streamlined game-keeping in a 100+ annual Boccia matches by developing a modern, internationally regulation-compliant match-keeping app using Swift, Objective-C, SwiftUI, and the Core Data framework.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {ArcGIS Mapping Team Leader}{Aug. 2022 -- May 2023}
      {State Botanical Garden of Georgia}{Athens, GA}
      \resumeItemListStart
        \resumeItem{Decreased data logging time by 90\% by engineering a data pipeline using Python and the OpenPyXL library to automate the plotting of 11,047 taxa into an ArcGIS map.}
        \resumeItem{Facilitated the visits of 230,000+ annual visitors by coordinating the team's collection of new Narcissus field data and updating the public garden map.}
    \resumeItemListEnd



  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Gran Turismo 7 Predictor} $|$ \emph{Python, Scikit-learn}}{May 2024 -- Present}
          \resumeItemListStart
            \resumeItem{Achieve a accuracy of 70\% for final position prediction for the Gran Turismo 7 racing game.}
            \resumeItem{Train a Naive Bayes classifier and stream game data from the granturismo library.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

    
%-----------PUBLICATIONS-----------
\section{Publications}
    \resumeSubHeadingListStart
    \small{\item{
     \textbf{}{Zhu, M., Kanjiani, R., Lu, J., Choi, A., Ye, Q., \& Zhao, L. (2024). LatentExplainer: Explaining latent representations in deep generative models with multi-modal foundation models. Paper presented at the Conference on Empirical Methods in Natural Language Processing, Miami, FL. [Submitted]}
    }}
    \resumeSubHeadingListEnd


%-----------Leadership-----------
\section{Leadership}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Advising Fellow Leadership Team Member}{Apr. 2023 -- June 2024}
      {Matriculate}{Atlanta, GA}
      \resumeItemListStart
        \resumeItem{Achieved 20\% higher advisor applications than last year through email and personal outreach.}
        \resumeItem{Supported 3 high school students apply for college and financial aid through essay reviews and weekly meetings.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Honors and Certifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{}{Presidential Scholar (1 Semester), Dean’s List (1 Semester), International Baccalaureate Diploma Recipient, Honors Diploma Recipient.} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
