%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


% ----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\myResumeProjectHeading}[3]{
	\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
      \textit{\small#3} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Raasikh Kanjiani} \\ \vspace{1pt}
    \small 404-428-8533 $|$ \href{mailto:raasikh.kanjiani@gmail.com}{raasikh.kanjiani@gmail.com} $|$ 
    \href{https://linkedin.com/in/raasikhk}{linkedin.com/in/raasikhk} $|$
    \href{https://github.com/Student9676}{github.com/Student9676} $|$
	\href{https://huggingface.co/raasikhk}{huggingface.co/raasikhk}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Emory University}{Atlanta, GA}
      {Bachelor of Science in Computer Science, Minor in Mathematics}{Aug. 2023 -- May 2026}
        \vspace{0pt}
      \resumeSubheading
      {University of Georgia}{Athens, GA}
      {Bachelor of Science in Computer Science, New Media Certificate}{Aug. 2022 -- May 2023}
      \vspace{1pt}
    \small{\item{
     \textbf{Coursework: }{Artificial Intelligence, Machine Learning, Data Structures and Algorithms, Multivariable Calculus, Linear Algebra, Systems Programming, Computer Architecture.} \\ 
     \vspace{4pt}
     \textbf{Programming Languages: }{Python (Proficient), Java (Proficient), Swift (Intermediate), C (Intermediate),\newline R (Intermediate), Unix/Linux (Proficient), Emacs, Objective-C, Assembly, JavaScript, SQL, Lua, Latex.}
    }}
    
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Technical Research Intern}{June 2024 -- Present}
      {NSF REU at Emory University}{Atlanta, GA}
      \resumeItemListStart
        \resumeItem{Developing a literature survey generator, utilizing graph data of 690,000+ papers and 10,000+ reviews.}
		\resumeItem{Implementing a RAG-based querying system to extract relevant data from papers for survey generation.}
        \resumeItem{Adapting recently published models and researching metrics to compare and quantify the model's performance.}
      \resumeItemListEnd
	  \resumeItem{\textbf{Publication:} Zhu, M., \textbf{Kanjiani, R.}, et al. (2024). LatentExplainer: Explaining latent representations in deep generative models with multi-modal foundation models. [Submitted to EMNLP 2024]}


    \resumeSubheading
      {App Development Intern}{Jan. 2024 -- May 2024}
      {USA Boccia}{Remote}
      \resumeItemListStart
        \resumeItem{Built an internationally compliant game-keeping iOS app to streamline 500+ annual Boccia games using Swift.}
		\resumeItem{Constructed a back end using the Core Data framework to efficiently save and restore match history data locally.}
		\resumeItem{Designed a scoreboard UI to be cast onto external displays, simplifying match tracking for 7500+ viewers.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {ArcGIS Mapping Intern}{{Aug. 2022 -- May 2023}}
      {The State Botanical Garden of Georgia}{Athens, GA}
      \resumeItemListStart
        \resumeItem{Automated plotting of 11,047 taxa into an ArcGIS map by devising new data collection and organization methods.}
        \resumeItem{Decreased data logging time by 90\% by engineering a data pipeline using Python and the OpenPyXL library.}
		\resumeItem{Supervised a team of three in collecting new field data for 300+ flowers, facilitating the visits of 230,000+ visitors.}    
		\resumeItemListEnd



  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
	\myResumeProjectHeading
	{\href{https://github.com/Student9676/carlos-artifact-tagging-bias}{\textbf{Museum Artifact Description Debiaser}} $|$ \emph{Python, Transformers, PyTorch, React, Django}}{June 2024 -- Present}
		  {Project Lead}
          \resumeItemListStart
            \resumeItem{Fine-tuning Google's BERT model to detect language bias and jargon in artifact descriptions with 83\% accuracy.}
            \resumeItem{Creating a custom ChatGPT chatbot to help the staff replace biases with inclusive language before publication.}
			\resumeItem{Developing a full-stack web application using React and Django to showcase the model pipeline and findings.}
          \resumeItemListEnd

      \myResumeProjectHeading
	{\href{https://github.com/Student9676/gt7predictor}{\textbf{Gran Turismo 7 Race Predictor}} $|$ \emph{Python, Swift, Sklearn}}{May 2024 -- Present}
          {Personal Project}
		  \resumeItemListStart
		  \resumeItem{Training a Naive Bayes classifier to predict final race positions with 70\% accuracy in the Gran Turismo 7 game.}
		  \resumeItem{Designing a data pipeline to stream live game data from the console to the app every millisecond for predictions.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

    
% %-----------PUBLICATIONS-----------
% \section{Publications}
%     \resumeSubHeadingListStart
%     \small{\item{
%     % \textbf{}{Zhu, M., Kanjiani, R., Lu, J., Choi, A., Ye, Q., \& Zhao, L. (2024). LatentExplainer: Explaining latent representations in deep generative models with multi-modal foundation models. Paper presented at the Conference on Empirical Methods in Natural Language Processing, Miami, FL. [Submitted]}\\
% 	 \textbf{}{Zhu, M., Kanjiani, R., Lu, J., Choi, A., Ye, Q., \& Zhao, L. (2024). LatentExplainer: Explaining latent representations in deep generative models with multi-modal foundation models. [Submitted]}
%     }}
%     \resumeSubHeadingListEnd


%-----------Leadership-----------
\section{Leadership}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Advising Fellow Team Leader}{Apr. 2023 -- June 2024}
      {Matriculate}{Remote}
      \resumeItemListStart
        \resumeItem{Achieved 20\% higher advisor applications than the previous year through personalized email and SMS outreach.}
        \resumeItem{Led weekly workshops and meetings to support 3 high school students apply for college and financial aid.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Honors and Certifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{}{NSF Grant Recipient, National Name Exchange Member, Presidential Scholar (1 Semester), Dean’s List (1 Semester), International Baccalaureate Diploma Recipient, Honors Diploma Recipient.} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
